Efficient Detection and Classification of Epigenomic Changes Under Multiple Conditions

### 2021-04-10 Latex/paper/paper.tex
Update text
Update ENCODE acronym

The data that support the findings of this paper are openly available in the ENCODE Project portal \citep{sloan2016encode} at https://www.encodeproject.org.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supporting Information}
Web Appendices A-D, referenced in Sections 1-6, and a link to the implemented software are available with this paper at the Biometrics website on Wiley Online Library. MACS2 peak caller is available at https://github.com/macs3-project/MACS. epigraHMM has been implemented as an R package and it is available for download at https://github.com/plbaldoni/epigraHMM. All of the scripts used in the analyses presented in
this paper can be downloaded at https://github.com/plbaldoni/epigraHMMPaper.

>>>>

The data that support the findings of this paper are openly available in the Encyclopedia of DNA Elements Project portal at https://www.encodeproject.org \citep{sloan2016encode}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supporting Information}
Web Appendices A-D, referenced in Sections 1-6, and a link to the implemented software are available with this paper at the Biometrics website on Wiley Online Library. MACS2 peak caller is available at https://github.com/macs3-project/MACS.

epigraHMM has been implemented as an R package and it is available for download at https://github.com/plbaldoni/epigraHMM. All of the scripts used in the analyses presented in this paper can be downloaded at https://github.com/plbaldoni/epigraHMMPaper.
